---
title: "DATA607_Project1"
author: "PeiMing Chen"
date: "`r Sys.Date()`"
output: pdf_document
---
Introduction: 
In this project, we were given a text file with chess tournament results where the information has some structure. My job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:

Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

I created a .CSV file including information of all the players that mentioned above.
```{r load-packages, message=FALSE}
library(tidyverse)
library(stringr)
library(dplyr)
```

### Read the Data text file 

This tournamnet .CSV file is saved in my Github account. The separator function," \t ", is applied. 

```{r}
tournamentData_info <- read.csv("https://raw.githubusercontent.com/PMCformosa/Project_1/main/tournamentinfo.txt", header = FALSE, sep="\t")
tournamentData_info
```

### Cleaning up the Data
Remove the headers 
```{r}
headingsoff_Data <- tournamentData_info [-c(1:3),]
headingsoff_Data
```

Select only the names of players from the original data
```{r}
player_name <- unlist(str_extract_all(headingsoff_Data,"\\| [[:upper:]]+ [[:upper:]]+ [[:upper:] -]+\\|"))
player_name

```

Clean up the names of players
```{r}
player_name <- str_replace_all(player_name, pattern = "\\| ", replacement = "")
name_only <- str_replace_all(player_name, pattern = " +\\|", replacement = "")
name_only
```

Selet only the states of players from the original data
```{r}
State_name <- unlist(str_extract_all(headingsoff_Data," [[:upper:]][[:upper:]] \\|"))
State_name
#View(State_name)
```

Clean up the states of players
```{r}
State_name <- str_replace_all(State_name, pattern = " \\|", replacement = "")
State_name <- str_replace_all(State_name, pattern = " ", replacement = "")
State_name
```

Select the total points of each player
```{r}
Total_Points_1 <- unlist(str_extract_all(headingsoff_Data,"\\|[[:digit:]].[[:digit:]]"))

Total_Points <- str_replace_all(Total_Points_1, pattern = "\\|", replacement = "")
Total_Points 
```

### Obtain Players' Pre-Rating 
```{r}
Player_preRating <- unlist(str_extract_all(headingsoff_Data,": +[[:digit:]]{3,}"))
 
Player_preRating  <- str_replace_all(Player_preRating, pattern = ": +", replacement = "")
Player_preRating
```

### Average Pre Chess Rating of Opponents

Select opponents of each player
```{r}
opponents <- unlist(str_extract_all(headingsoff_Data,"\\|[[:digit:]].[[:digit:]] +\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|[[:upper:]] +[[:digit:]]*\\|"))

opponents
```

Clean up the selected data
```{r}
opponents  <- str_sub(opponents, 7,-1)

opponents
```

Clean up the selected data further and make it a list 
```{r}
opponents_list  <- str_extract_all(opponents,"(\\d+)")
opponents_list
```

### Obtain the Average of Opponents' Pre Chess Rating of each player
```{r}
rating <- unlist(lapply(Player_preRating,strtoi))
all_avg_rate = c()
for (x in opponents_list) {
  each_player_opponent <- unlist(lapply(x,strtoi))
  each_player_opponent_rate <- c()
  for (y in each_player_opponent) {
    each_player_opponent_rate <- append(each_player_opponent_rate,rating[y])
  }
  avg_rate <- mean(each_player_opponent_rate)
  #print(avg_rate)
  all_avg_rate <- append(all_avg_rate,avg_rate)
  #print(all_avg_rate)
}

all_avg_rate
```

Rearrange all the cleaned up data into a table 
```{r}
player_number <- unlist(str_extract_all(tournamentData_info, "\\d{1,2}\\s\\|"))
player_number <- str_replace_all(player_number, pattern = "(\\s\\|)", replacement = "")
player_number <- as.numeric(player_number)
player_number 
tableA <- data.frame(player_number = player_number, name_only = name_only, State_name = State_name, Total_Points  = Total_Points , Player_preRating = rating, Opponent_average_rating_list = all_avg_rate)
tableA
view(tableA)
```

Save the data table into a .CSV file and upload it on my github account
```{r}
write.csv(tableA, "tableA.csv", row.names=TRUE)
```

